Manuscript

### 2015-02-20 inst/simulation/manuscript.Rmd
...

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
#print(p)
saveFigure(p, "manuscript-figure-1.png", width=8, height=5)

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE, log=FALSE) {
  ddply(data.frame(scenario=scenarios, year=rep(year, scenarios), iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

@@

    estimates$data <- subset(estimates$data, year == x$year)
    #if (log) estimates$data$fittedMean <- log(estimates$data$fittedMean)
    density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- year0

@@

p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent", guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2))))) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) + theme(legend.position="bottom")
print(p)
saveFigure(p, "manuscript-figure-2a.png", width=6,height=3)

@@

p <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0,0)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() + theme(panel.grid.major=element_line(colour="grey"))
print(p)
saveFigure(p, "manuscript-figure-2b.png", width=6,height=3)
```

@@

cutoff <- 1000
cutoffPopulationSizes <- function(populationSizes, cutoff=Inf) subset(populationSizes, Estimated <= cutoff)

@@

plotLogPopulationSize <- function(size, modelName, xlim, ylim, cutoff) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize <- getMeanPopulationSizes(size)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=12))

@@

@@

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[4]), subset(logMeanPopulationSizes, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

#xlim <- log10(10^c(2,4)); ylim <- xlim
xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), subset(logMeanPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), subset(logMeanPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), subset(logMeanPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[4]), subset(logMeanPopulationSizes10Days, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png", width=8, height=4)
```

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated > overEstimate) / nrow(x)) * 100)
    x <- subset(x, Estimated <= overEstimate)
    if (x$modelName[1] == "FMPModel") failed <- NA
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), MeanProp=prop.mean, SDProp=prop.sd, Failed=failed))
  }, overEstimate=overEstimate)

  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  #y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)

  z <- z[,c("Scenario","Model","Slope","R2","MeanProp","SDProp","Failed")]
  #z$EstDev <- round(z$EstDev, 2)
  z$MeanProp <- round(z$MeanProp, 2)
  z$SDProp <- round(z$SDProp, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

writeTable <- function(df, filename, context) {
  library(ReporteRs)
  doc <- docx()
  flextable <- FlexTable(df)
  addFlexTable(doc, flextable)
  dir <- normalizePath(context$figuresDirectory)
  writeDoc(doc, file=file.path(dir, filename))
}

@@

#dir <- normalizePath(context$figuresDirectory)
#write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
#write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
#write.csv(logTable3, file=file.path(dir, "table-3a.csv"))

writeTable(subset(logTable1, Model != "VT"), "table-1a.docx", context)
writeTable(subset(logTable2, Model != "VT"), "table-1b.docx", context)
writeTable(subset(logTable3, Model != "VT"), "table-1c.docx", context)
```

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersectionsx <- plyr::join(populationSizes, intersections)
intersections2000x <- plyr::join(populationSizes2000, intersections2000)
intersections10daysx <- plyr::join(populationSizes10Days, intersections10days)
#i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
#                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
#                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
#ddply(intersectionsx, .(Scenario, modelName), i.stat)
#ddply(intersections2000x, .(Scenario, modelName), i.stat)
#ddply(intersections10daysx, .(Scenario, modelName), i.stat)

rer.stat <- function(x) data.frame(RERMean=round(mean(x$intersections/x$Observed),2), RERSD=round(sd(x$intersections/x$Observed),2))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario)
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario)
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario)

writeTable(i, "table-2a.docx", context)
writeTable(i2000, "table-2b.docx", context)
writeTable(i10days, "table-2c.docx", context)
```

@@

plotPopulationCorrelations <- function(populationCorrelations) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1)
saveFigure(p1, "manuscript-figure-4a.png", width=4, height=4)
p2 <- plotPopulationCorrelations(pc2)
saveFigure(p2, "manuscript-figure-4b.png", width=4, height=4)
p3 <- plotPopulationCorrelations(pc3)
saveFigure(p3, "manuscript-figure-4c.png", width=4, height=4)
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

@@

#cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[1:3], panel="a", scenarioNames=scenarios)
#cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1:3], panel="b", scenarioNames=scenarios)
#cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1:3], panel="c", scenarioNames=scenarios)

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)

#p1 <- plotCIProportions(cip1)
#saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
#p2 <- plotCIProportions(cip2)
#saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
#p3 <- plotCIProportions(cip3)
#saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)
```

>>>>

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
#print(p)
#saveFigure(p, "manuscript-figure-1.png", width=8, height=5)
saveFigure(p, "manuscript-figure-1.png", width=17, height=15, dpi=200) # draft quality

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE, log=FALSE) {
  ddply(data.frame(scenario=scenarios, year=rep(year, length(scenarios)), iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

@@

    estimates$data <- subset(estimates$data, year == x$year)
    #if (log) estimates$data$fittedMean <- log(estimates$data$fittedMean)
    density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- x$year

@@

p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent", guide=guide_legend(title=expression(paste("Population density ", (log[10]~individuals/km^2)))), trans="log10", breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5), labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=(10^-4.5, 10^-2.5)) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) + theme(legend.position="bottom")
#print(p)
#saveFigure(p, "manuscript-figure-2a.png", width=6,height=3)
saveFigure(p, "manuscript-figure-2a.png", width=17, height=8, dpi=200) # draft quality

@@

p <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0,0)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() + theme(panel.grid.major=element_line(colour="grey"))
print(p)
#saveFigure(p, "manuscript-figure-2b.png", width=6,height=3)
saveFigure(p, "manuscript-figure-2b.png", width=17, height=8, dpi=200) # draft quality

@@

cutoffPopulationSizes <- function(populationSizes, cutoff=c(0,Inf)) subset(populationSizes, cutoff[1] <= Estimated & Estimated <= cutoff[2])

@@

plotLogPopulationSize <- function(size, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize <- getMeanPopulationSizes(size)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        plot.margin=unit(c(0, 0, 0, 0), units="line"), #top, right, bottom, and left margins
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

cutoff <- c(1,1000)

@@

xlim <- log10(c(1,6000)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png")

p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png")
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png")
```

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((1 - nrow(cutoffPopulationSizes(x, overEstimate)) / nrow(x)) * 100)
      #(sum(x$Estimated < overEstimate[1] | x$Estimated > overEstimate[2]) / nrow(x)) * 100)
    x <- cutoffPopulationSizes(x, overEstimate)
    #subset(x, Estimated <= overEstimate)
    #if (x$modelName[1] == "FMPModel") failed <- NA
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, EstTrue=NA, EstTrueSD=NA, N=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), EstTrue=prop.mean, EstTrueSD=prop.sd, Failed=failed, N=nrow(x)))
  }, overEstimate=overEstimate)

  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- prettyScenario(z$Scenario) #substr(z$Scenario, 1, 1)
  if (full) return(z)

  z <- z[,c("Scenario","Model","Slope","R2","EstTrue","EstTrueSD","Failed","N")]
  #z$MeanProp <- round(z$MeanProp, 2)
  #z$SDProp <- round(z$SDProp, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

#writeTable <- function(df, filename, context) {
#  library(ReporteRs)
#  doc <- docx()
#  flextable <- FlexTable(df)
#  addFlexTable(doc, flextable)
#  dir <- normalizePath(context$figuresDirectory)
#  writeDoc(doc, file=file.path(dir, filename))
#}

plotPopulationSizesTable <- function(logTable) {
  library(reshape2)
  x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("Slope", "R2", "EstTrue", "Failed"))
  p <- ggplot(x, aes(Scenario, value, group=Model)) + geom_point(aes(shape=Model)) + geom_line() +
    facet_grid(variable~Case, scales="free_y") + ylab("") +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=10),
                                        strip.text.y=element_text(size=10), legend.position="bottom",
                                        plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
                                        legend.margin=unit(0, units="line"))# , legend.key=element_rect(fill="transparent"))
  return(p)
}

@@

logTable1$Case <- "a"
logTable2$Case <- "b"
logTable3$Case <- "c"
logTable <- rbind(subset(logTable1, Model != "VT"), subset(logTable2, Model != "VT"), subset(logTable3, Model != "VT"))
p <- plotPopulationSizesTable(logTable)
saveFigure(p, "manuscript-figure-3.png", width=17, height=17, dpi=200)

#writeTable(subset(logTable1, Model != "VT"), "table-1a.docx", context)
#writeTable(subset(logTable2, Model != "VT"), "table-1b.docx", context)
#writeTable(subset(logTable3, Model != "VT"), "table-1c.docx", context)
```

```{r table-2}
plotIntersectionPopulationSizeTable <- function(ratioTable) {
  library(reshape2)
  library(grid)
  x <- melt(ratioTable, id.vars=c("Scenario", "Case"), measure.vars=c("SizeCount"))
  p <- ggplot(x, aes(Scenario, value, group=Case)) + geom_point(aes(shape=Case)) + geom_line() +
    ylab("") + #guides(shape=guide_legend()) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=10),
                                        strip.text.y=element_text(size=10), legend.position="bottom",
                                        plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))# , legend.key=element_rect(fill="transparent"))
  return(p) 
}
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png")

intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections10days$intersections <- intersections10days$intersections / 10
intersectionsx <- plyr::join(populationSizes, intersections)
intersections2000x <- plyr::join(populationSizes2000, intersections2000)
intersections10daysx <- plyr::join(populationSizes10Days, intersections10days)

rer.stat <- function(x) data.frame(SizeCount=round(mean(x$intersections/x$Observed),2), SizeCountSD=round(sd(x$intersections/x$Observed),2))
i <- ddply(intersectionsx, .(Scenario), rer.stat); i$Scenario=prettyScenario(i$Scenario); i$Case <- "a"
i2000 <- ddply(intersections2000x, .(Scenario), rer.stat); i2000$Scenario=prettyScenario(i2000$Scenario); i2000$Case <- "b"
i10days <- ddply(intersections10daysx, .(Scenario), rer.stat); i10days$Scenario=prettyScenario(i10days$Scenario); i10days$Case <- "c"

iall <- rbind(i, i2000, i10days)
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png")

#writeTable(i, "table-2a.docx", context)
#writeTable(i2000, "table-2b.docx", context)
#writeTable(i10days, "table-2c.docx", context)
```

@@

plotPopulationCorrelations <- function(populationCorrelations) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
                                      legend.margin=unit(0, units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1)
saveFigure(p1, "manuscript-figure-4a.png")
p2 <- plotPopulationCorrelations(pc2)
saveFigure(p2, "manuscript-figure-4b.png")
p3 <- plotPopulationCorrelations(pc3)
saveFigure(p3, "manuscript-figure-4c.png")
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, -.5, -.5), units="line"),
          legend.margin=unit(0, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom")
  return(p)
}
```

@@

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)
```
